{\helveticaitalic{Supplementary Material}}

### 2022-03-07 tex/supplementary.tex
Refactor a bunch of plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when producing your supplementary material for your Frontiers article.                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 2.5 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

@@

\section{Model equations and parameters}
The asymptotic functions $m_{\infty}$ and $w_{\infty}$ for the calcium and potassium conductances, respectively, are given by
\begin{align}
  m_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{A})/v_{B}\right)}\right),\\
  w_{\infty}(v_{i}) &= \frac{1}{2}\left(1+\tanh{\left((v_{i}-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
  \caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
  \centering
  \begin{tabular}{ll}
    Parameter & value\\
    \hline
              & \\
    $g_{\leak}$ & $0.15$ \si{mS/cm^2}\\
    $g_{\ca}$ & $0.3$ \si{mS/cm^2}\\
    $g_{\k}$ & $0.6$ \si{mS/cm^2}\\
    $v_{\leak}$ & $-50$ \si{mV}\\
    $v_{\ca}$ & $100$ \si{mV}\\
    $v_{\k}$ & $-70$ \si{mV}\\
    $v_{A}$ & $1$ \si{mV}\\
    $v_{B}$ & $14.5$ \si{mV}\\
    $v_{C}$ & $4$ \si{mV}\\
    $v_{D}$ & $15$ \si{mV}\\
    $I$ & $3.8$ \si{\mu A/cm^2}\\
    $\tau_w$ & $100$ \si{ms}\\
    $\tau_a$ & $1000$ \si{ms}\\
    $\tau_b$ & $100$ \si{ms}\\
    $\tau_\kappa$ & $100$ \si{ms}\\
    $\tau_\gamma$ & $0.0001$ \si{ms}\\
    $v_{\theta}$ & $0$ \si{mV}\\
    $v_{s}$ & $-80$ \si{mV}\\
    $T$ & $376$ \si{ms}\\
    $T_{act}$ & $49$ \si{ms}\\
    $T_{inact}$ & $327$ \si{ms}\\
    $\gstar$ & $0.0036$ \si{mS/cm^2}\\
    $\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$\\
    $\rho:=\exp(-T_{inact}/\tau_a)$ & $0.721$\\
  \end{tabular}
\end{table}

@@

% \bibliographystyle{frontiersinSCNS_ENG_HUMS} %  for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{bibliography.bib}

>>>>

@@

\section{Model equations and parameters}
The asymptotic function for the calcium conductance $m_{\infty}$ is given by
\begin{equation}
	m_{\infty}(v) = \frac{1}{2}\left(1+\tanh{\left((v-v_{A})/v_{B}\right)}\right).
\end{equation}
The voltage and potassium nullclines, \(v_{\infty}(v)\) and \(w_{\infty}(v)\), are
\begin{align}
	v_{\infty}(v) & = \frac{-g_{l}(v-v_{l}) - g_{ca}m_{\infty}(v)(v-v_{ca}) + I - \bar g s(v-v_{s})}{g_{k}(v-v_{k})},
	\\
	w_{\infty}(v) & = \frac{1}{2}\left(1+\tanh{\left((v-v_{C})/v_{D}\right)}\right).
\end{align}
Model parameters were adapted from~\cite{bose2011} and are given in \cref{tab:pars}:
\begin{table}[h]
	\caption{Default parameters for coupled Morris-Lecar model.~\label{tab:pars}}
	\centering
	\begin{tabular}{ll}
		Parameter                        & value                 \\
		\hline
		                                 &                       \\
		$g_{\leak}$                      & $0.15$ \si{mS/cm^2}   \\
		$g_{\ca}$                        & $0.3$ \si{mS/cm^2}    \\
		$g_{\k}$                         & $0.6$ \si{mS/cm^2}    \\
		$v_{\leak}$                      & $-50$ \si{mV}         \\
		$v_{\ca}$                        & $100$ \si{mV}         \\
		$v_{\k}$                         & $-70$ \si{mV}         \\
		$v_{A}$                          & $1$ \si{mV}           \\
		$v_{B}$                          & $14.5$ \si{mV}        \\
		$v_{C}$                          & $4$ \si{mV}           \\
		$v_{D}$                          & $15$ \si{mV}          \\
		$I$                              & $3.8$ \si{\mu A/cm^2} \\
		$\tau_w$                         & $100$ \si{ms}         \\
		$\tau_a$                         & $1000$ \si{ms}        \\
		$\tau_b$                         & $100$ \si{ms}         \\
		$\tau_\kappa$                    & $100$ \si{ms}         \\
		$\tau_\gamma$                    & $0.0001$ \si{ms}      \\
		$v_{\theta}$                     & $0$ \si{mV}           \\
		$v_{s}$                          & $-80$ \si{mV}         \\
		$T$                              & $376$ \si{ms}         \\
		$T_{act}$                        & $49$ \si{ms}          \\
		$T_{inact}$                      & $327$ \si{ms}         \\
		$\gstar$                         & $0.0036$ \si{mS/cm^2} \\
		$\lambda:=\exp(-T_{act}/\tau_b)$ & $0.612$               \\
		$\rho:=\exp(-T_{inact}/\tau_a)$  & $0.721$               \\
	\end{tabular}
\end{table}

@@

\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{bibliography.bib}
